Viscous Erosion in Porous Media

### 2018-03-13 docs/methods/erosion_methods.tex
made small changes throughout

Because of the length and velocity scales of groundwater flow, we
restrict our attention to small Reynolds number flows.  For groundwater
flow, Darcy's law is often used, but this does not resolve the pore
structure and assumes a homogeneous geometry which is often not valid.
Instead, we use the incompressible Stokes equations to represent the
flow, and the individual pores are resolved which results in a complex
multiply-connected geometry.  A boundary integral equation (BIE) is
well-suited for solving the incompressible Stokes equations in a complex
geometry since it can resolve individual grains and the non-negligible
interactions between bodies are resolved. Moreover, high-order accuracy
and computational efficiency are obtained. To link the eroding body and
fluid dynamics, the body is eroded in the normal direction at a rate
that is proportional to the magnitude of the shear
stress~\cite{ris-moo-chi-she-zha2012}.  Tracking the interface of
fluid-structure interaction problems with a long time horizon is
particularly (???) ---the mesh is often distorted and tangled by the dynamics
and regions of high curvature develop.  These two issues are resolved
by, first, introducing a tangential velocity field to maintain a grid
that is equispaced in arc length, but that does not affect the dynamics,
and, second, a curvature penalization term.  Furthermore, the frame of
reference is changed to \thL~variables so that the curvature term
appears as a diffusive term that can easily be handled in a 
numerically stable fashion, e.g.~via an exponential integrator or an implicit method.

@@

To evolve the boundaries of eroding bodies, we use the {\thL} framework which offers certain advantages in numerically stabilizing moving-interface problems \cite{hou-low-she1994}. Here, $\theta$ is the local tangent angle and $L$ is the total perimeter of a given boundary. For a boundary parametrized by arc length $(x(s),y(s))$, the local tangent angle is defined through the relation $\left( \pdi{x}{s}, \pdi{y}{s} \right) = \left(\cos \theta, \sin \theta \right)$.

@@

In the following, we parameterize each boundary by normalized arc length, $\alpha = 2 \pi s / L$. In terms of $\alpha$, the curvature is given by
\begin{align}
\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha} \, ,
\end{align}
and substitution into~\eqref{eqn:Vn} gives
\begin{align}
\label{eqn:Vn2}
\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1 \right) \, .
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Post processing quantities of interest}
\label{s:qoi}
To study characteristics of the flow, the vorticity
(Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}),
and drag (Section~\ref{sec:drag}) will be computed.  Once
equation~\eqref{eqn:completed_DLP} is solved for the density function,
Stokeslets, and rotlets, all of these quantities can be computed.  For
target points in the fluid domain, the resulting layer potentials
involve integrands that are periodic, so the trapezoid rule guarantees
spectral accuracy since the integrand is smooth~\cite{tre-wei2014}.
However, if the target point is close to a boundary, a nearly-singular
integrand must be integrated, and this requires upsampling that is
described in Section~\ref{sec:NSI}.  When the target points is on the
boundary, the integrands involve singularities that are evaluated by
combining singularity subtraction and odd-even
integration~\cite{sid-isr1988}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pressure}
\label{sec:pressure}
To compute the pressure at $\xx \in \Omega$, we follow the
same procedure used for the shear stress.  We start by computing the
pressure of the double-layer potential for $\xx \in \Omega$ and add the
appropriate jump if $\xx \in \Gamma$. For $\xx \in \Omega$, the pressure
is
\begin{align}
  p^{D}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot \eeta(\yy) \,ds_\yy.
    \label{eqn:pressureDLP}
\end{align}
The pressure due to the Stokeslets is
\begin{align}
  p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
  \label{eqn:shearPressureSR}
\end{align}
and the pressure due to the rotlets is zero.  Therefore, the pressure is
\begin{align*}
  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), \quad &&\xx \in \Omega,\\
  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
              p^{S}(\xx), && \xx \in \bd\Omega.
\end{align*}
To compute~\eqref{eqn:pressureDLP} numerically, we apply the trapezoid
rule with an upsampling scheme described in Section~\ref{sec:NSI}.

To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
as $\xx$ tends to $\xx_0$.  The limiting value is given
by~\cite{qua-bir2014a}
\begin{align}
  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
  \label{eqn:pressureJump}
\end{align}
Similar to the shear stress, the singularity of the pressure
corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is
too strong for the trapezoid rule to be directly applied.  Therefore, we
again subtract a constant density function and write the pressure as
\begin{align*}
  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy, 
    \quad \xx \in \bd\Omega
\end{align*}
Then, identical to how the shear stress is
computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
evaluate this layer potential for pressure.  The pressure due to the
Stokeslets are given in equation~\eqref{eqn:shearPressureSR}.  Finally,
to add the jump condition~\eqref{eqn:pressureJump}, Fourier
differentiation is used to compute the arclength derivative.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Near-singular integration}
\label{sec:NSI}
The layer potentials for the~\eqref{eqn:velocityDLP},
vorticity~\eqref{eqn:vorticityDLP}, and pressure~\eqref{eqn:pressureDLP}
need to be evaluated at points $\xx \in \Omega$. We write the general
layer potential as
\begin{align}
  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) ds_\yy.
  \label{eqn:genericLP}
\end{align}
Since the integrand is periodic and smooth, the trapezoid rule
guarantees spectral accuracy.  However, when the target point $\xx$ is
close to $\bd\Omega$, the integrand is nearly-singular, and the accuracy
of the trapezoid rule deteriorates unless a large number of
discretization points are used.  We are only interested in computing the
velocity, vorticity, and pressure to visualize the flow, so it is not
necessary that we resolve the integrands for arbitrarily close target
points

The layer potential~\eqref{eqn:genericLP} is approximated with the
trapezoid rule 
\begin{align}
  \phi(\xx) = \sum_{j=1}^N q_j K(\xx,\yy_j),
  \label{eqn:layerPotential}
\end{align}
where $q$ contains the quadrature weights, Jacobian, and density
function.  Based on numerical experiments, the error of the $N$-point
trapezoid rule is acceptable for points $\xx$ that are more than 5
arclength spacings from $\bd\Omega$.

For points that are closer than 5 arclength spacings to $\bd\Omega$, we
use an upsampled trapezoid rule.  The required upsampling of the
geometry and the density function is done with a Fourier interpolant.
To minimize the number of discretization points that are used to
approximate the layer potential~\eqref{eqn:layerPotential}, we use the
same upsampling rate for all target points that are in the same dyadic
interval (Table~\ref{tbl:upsampling}).  For points that are closer than
$5/16$ of an arclength from $\bd\Omega$, a value of 0 is simply assigned
to $\phi$.
\newcolumntype{V}{>{\centering\arraybackslash}m{4em}}
\newcolumntype{N}{@{}m{0pt}@{}}
\begin{table}[htpb]
\centering
%\begin{tabular}{|c|ccccc|}
\begin{tabular}{|V|V|V|V|V|V|N}
  \hline
  $d(\xx,\bd\Omega)$ &
  $[5h,\infty]$ &
  $[\frac{5}{2}h,5h]$ &
  $[\frac{5}{4}h,\frac{5}{2}h]$ & 
  $[\frac{5}{8}h,\frac{5}{4}h]$ &
  $[\frac{5}{16}h,\frac{5}{8}h]$ & \\ [2ex] 
  \hline
  Upsample Rate & 1 & 2 & 4 & 8 & 16 & \\
  \hline
\end{tabular}
\caption{\label{tbl:upsampling}The upsampling rate used in our
near-singular integration scheme.  $d(\xx,\bd\Omega)$ is the distance
between a points $\xx \in \Omega$ and the boundary of the domain
$\bd\Omega$, and $h$ is an arclength spacing.}
\end{table}

In future work, upsampling will not be adequate.  For example, if
eroding bodies are also sedimenting, bodies will come too close to one
another for upsampling to only used.  Therefore, we plan to implement a
near-singular integration scheme that uses either near-singular
interpolation~\cite{qua-bir2014a}, quadrature by
expansion~\cite{klo-bar-gre-one2013}, Barycentric
interpolation~\cite{bar-wu-vee2015}, or panel-based
quadrature~\cite{hel-oja2008a}.

@@

Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points and shown at three evenly spaced times. Here, color represents the vorticity of the surrounding flow. When evaluated on the boundary, vorticity corresponds to the shear stress and thus the local erosion rate. As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity above and below it. The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, with vorticity vanishing at the body's front and rear stagnation points. 
At the next instance, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry. The greatest material loss has occurred at the body's top and bottom, where shear is strongest. Interestingly, the body has developed well-defined corners at its front and rear stagnation points. This geometric feature is a consequence of the erosion law, which depends on the {\em absolute} shear stress: wherever the stress vanishes, $\atau$ exhibits a corner, which manifests as a corner in the geometry. As shown in the third snapshot, this corner persists as the bodies becomes even more slender and continues to shrink. In this simulation, the body completely vanishes at a final time of $t_f = 1.79E-2$.

To better understand the shape evolution, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times. The interfaces are color-coded by normalized time $t/t_f$. The body seems to converge to a shape that resembles an American football --- a fairly slender, for-aft symmetric shape with corners at the front and back.
Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces. The normalized arc length $s/L$ runs counterclockwise around the body, with $s/L = 0$ corresponding to the rear stagnation point and $s/L = 0.5$ the front stagnation point. At early times (yellow to orange), the stress is distributed non-uniformly, with highest values at the top and bottom of the body. As time proceeds, though, the stress becomes more evenly distributed along the body's surface (red). As the body nears the final stages of erosion (dark red), the stress actually becomes slightly higher near the stagnation points. A close look reveals that the stress always vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/shrink_intface.pdf}
\caption{
Shape and stress evolution: (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals. Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes. (b) The distribution of absolute shear stress, $\atau$, along each of these interfaces. Normalized arc length, $s/L$, runs counterclockwise from the rear stagnation point. The stress initially varies over the body's surface, but becomes more uniform over time.}
\label{shrink_intface}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0

>>>>

Because of the length and velocity scales of groundwater flow, we
restrict our attention to small Reynolds number flows.  For groundwater
flow, Darcy's law is often used, but this does not resolve the pore
structure and assumes a homogeneous geometry which is often not valid.
Instead, we use the incompressible Stokes equations to represent the
flow, and the individual pores are resolved which results in a complex
multiply-connected geometry.  A boundary integral equation (BIE) is
well-suited for solving the incompressible Stokes equations in a complex
geometry since it can resolve individual grains and the non-negligible
interactions between bodies are resolved. Moreover, high-order accuracy
and computational efficiency are obtained. To link the eroding body and
fluid dynamics, the body is eroded in the normal direction at a rate
that is proportional to the magnitude of the shear
stress~\cite{ris-moo-chi-she-zha2012}.  Tracking the interface of
fluid-structure interaction problems with a long time horizon is
particularly (???) ---the mesh is often distorted and tangled by the dynamics
and regions of high curvature develop.  These two issues are resolved
by, first, introducing a tangential velocity field to maintain a grid
that is equispaced in arclength, but that does not affect the dynamics,
and, second, a curvature penalization term.  Furthermore, the frame of
reference is changed to \thL~variables so that the curvature term
appears as a diffusive term that can easily be handled in a 
numerically stable fashion, e.g.~via an exponential integrator or an implicit method.

@@

To evolve the boundaries of eroding bodies, we use the {\thL} framework which offers certain advantages in numerically stabilizing moving-interface problems \cite{hou-low-she1994}. Here, $\theta$ is the local tangent angle and $L$ is the total perimeter of a given boundary. For a boundary parametrized by arclength $(x(s),y(s))$, the local tangent angle is defined through the relation $\left( \pdi{x}{s}, \pdi{y}{s} \right) = \left(\cos \theta, \sin \theta \right)$.

@@

In the following, we parameterize each boundary by normalized arclength, $\alpha = 2 \pi s / L$. In terms of $\alpha$, the curvature is given by
\begin{align}
\kappa = \frac{2 \pi}{L} \pderiv{\theta}{\alpha} \, ,
\end{align}
and substitution into~\eqref{eqn:Vn} gives
\begin{align}
\label{eqn:Vn2}
\Vn = \atau +  \eps \mean{\atau}   \left(\pderiv{\theta}{\alpha} - 1 \right) \, .
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Post processing quantities of interest}
\label{s:qoi}
To study characteristics of the flow, the vorticity
(Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}),
and drag (Section~\ref{sec:drag}) will be computed.  Once
equation~\eqref{eqn:completed_DLP} is solved for the density function,
Stokeslets, and rotlets, all of these quantities can be computed.  For
target points in the fluid domain, the resulting layer potentials
involve integrands that are periodic and smooth, so the trapezoid rule
guarantees spectral accuracy~\cite{tre-wei2014}.  However, if the target
point is close to $\bd \Omega$, a nearly-singular integrand must be
integrated, and this requires upsampling that is described in
Section~\ref{sec:NSI}.  When the target points is on the boundary, the
integrands involve singularities that are evaluated by combining
singularity subtraction and odd-even integration~\cite{sid-isr1988}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Pressure}
\label{sec:pressure}
To compute the pressure at $\xx \in \Omega$, we follow the
same procedure used for the shear stress.  We start by computing the
pressure of the double-layer potential for $\xx \in \Omega$ and add the
appropriate jump if $\xx \in \Gamma$. For $\xx \in \Omega$, the pressure
is
\begin{align}
  p^{\DD}(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot \eeta(\yy) \,ds_\yy.
    \label{eqn:pressureDLP}
\end{align}
The pressure due to the Stokeslets is
\begin{align}
  p^S(\xx_0) = \sum_{\ell=1}^{M}\frac{\rr \cdot \llambda_\ell}{2\pi\rho^2},
  \label{eqn:shearPressureSR}
\end{align}
and the pressure due to the rotlets is zero.  Therefore, the pressure is
\begin{alignat*}{3}
  p(\xx) &= p^{\DD}(\xx) + p^{S}(\xx), &&\xx \in \Omega,\\
  p(\xx) &= \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx) + 
              p^{S}(\xx), \quad && \xx \in \bd\Omega.
\end{alignat*}
To compute~\eqref{eqn:pressureDLP} numerically, we apply the trapezoid
rule with an upsampling scheme described in Section~\ref{sec:NSI}.

To compute the pressure at $\xx_0 \in \bd\Omega$, we consider the limit
as $\xx$ tends to $\xx_0$.  The limiting value is given
by~\cite{qua-bir2014a}
\begin{align}
  \lim_{\substack{\xx \rightarrow \xx_0 \\ \xx \in \Omega}}p^\DD(\xx) =  
    \pderiv{\eeta}{\ss} \cdot \ss + p^{\DD}(\xx_0).
  \label{eqn:pressureJump}
\end{align}
Similar to the shear stress, the singularity of the pressure
corresponding to the double-layer potential~\eqref{eqn:pressureDLP} is
too strong for the trapezoid rule to be directly applied.  Therefore, we
again subtract a constant density function and write the pressure as
\begin{align*}
  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot (\eeta(\yy) - \eeta(\xx)) \,ds_\yy, 
    \quad \xx \in \bd\Omega.
\end{align*}
Then, identical to how the shear stress is
computed~\eqref{eqn:stressOddEven}, odd-even integration is used to
evaluate this layer potential for pressure.  The pressure due to the
Stokeslets are given in equation~\eqref{eqn:shearPressureSR}.  Finally,
to add the jump condition~\eqref{eqn:pressureJump}, Fourier
differentiation is used to compute the arclength derivative.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Near-singular integration}
\label{sec:NSI}
The layer potentials for the velocity~\eqref{eqn:velocityDLP},
vorticity~\eqref{eqn:vorticityDLP}, and pressure~\eqref{eqn:pressureDLP}
need to be evaluated at points $\xx \in \Omega$. We write the general
layer potential as
\begin{align}
  \phi(\xx) = \int_{\bd\Omega} K(\xx,\yy) \eeta(\yy) ds_\yy.
  \label{eqn:genericLP}
\end{align}
Since the integrand is periodic and smooth, the trapezoid rule
guarantees spectral accuracy.  However, when the target point $\xx$ is
close to $\bd\Omega$, the integrand is nearly-singular, and the accuracy
of the trapezoid rule deteriorates unless a large number of
discretization points are used.  We are only interested in computing the
velocity, vorticity, and pressure to visualize the flow, so it is not
necessary that we resolve the integrands for arbitrarily close target
points.

The layer potential~\eqref{eqn:genericLP} is approximated with the
trapezoid rule 
\begin{align}
  \phi(\xx) = \sum_{j=1}^N q_j K(\xx,\yy_j),
  \label{eqn:layerPotential}
\end{align}
where $q$ contains the quadrature weights, Jacobian, and density
function.  Based on numerical experiments, the error of the $N$-point
trapezoid rule is acceptable for points $\xx$ that are more than 5
arclength spacings from $\bd\Omega$. For points that are closer than 5
arclength spacings to $\bd\Omega$, we use an upsampled trapezoid rule.
The required upsampling of the geometry and the density function is done
with a Fourier interpolant.  To minimize the number of discretization
points that are used to approximate the layer
potential~\eqref{eqn:layerPotential}, we use the same upsampling rate
for all target points that are in the same dyadic interval
(Table~\ref{tbl:upsampling}).  For points that are closer than $5/16$ of
an arclength from $\bd\Omega$, a value of 0 is simply assigned to
$\phi$.
\newcolumntype{V}{>{\centering\arraybackslash}m{4em}}
\newcolumntype{N}{@{}m{0pt}@{}}
\begin{table}[htpb]
\centering
%\begin{tabular}{|c|ccccc|}
\begin{tabular}{|V|V|V|V|V|V|N}
  \hline
  $d(\xx,\bd\Omega)$ &
  $\left[5h,\infty\right]$ &
  $\left[\frac{5}{2}h,5h\right]$ &
  $\left[\frac{5}{4}h,\frac{5}{2}h\right]$ & 
  $\left[\frac{5}{8}h,\frac{5}{4}h\right]$ &
  $\left[\frac{5}{16}h,\frac{5}{8}h\right]$ & \\ [2ex] 
  \hline
  Upsample Rate & 1 & 2 & 4 & 8 & 16 & \\
  \hline
\end{tabular}
\caption{\label{tbl:upsampling}The upsampling rate of our near-singular
integration scheme.  $d(\xx,\bd\Omega)$ is the distance between a point
$\xx \in \Omega$ and the boundary of the domain $\bd\Omega$, and $h$ is
an arclength spacing.}
\end{table}

In future work, upsampling will not be adequate.  For example, if
eroding bodies are also sedimenting, bodies will come too close to one
another for upsampling to be sufficient.  Therefore, we plan to
implement a near-singular integration scheme that uses either
near-singular interpolation~\cite{qua-bir2014a}, quadrature by
expansion~\cite{klo-bar-gre-one2013}, Barycentric
interpolation~\cite{bar-wu-vee2015}, or panel-based
quadrature~\cite{hel-oja2008a}.

@@

Figure \ref{01bodseq} shows the erosion of a single body, numerically simulated with $N_\iin = 1024$ discretization points and shown at three evenly spaced times. Here, color represents the vorticity of the surrounding flow. When evaluated on the boundary, vorticity corresponds to the shear stress and thus the local erosion rate. As seen in the left-most snapshot, the body is initially circular and has the strongest vorticity above and below it. The flow is for-aft symmetric as a result of the time-reversibility of the Stokes equations, with vorticity vanishing at the body's front and rear stagnation points. 
At the next instance, the body has lost material due to erosion, but remains for-aft symmetric due to the flow symmetry. The greatest material loss has occurred at the body's top and bottom, where shear is strongest. Interestingly, the body has developed well-defined corners at its front and rear stagnation points. This geometric feature is a consequence of the erosion law, which depends on the {\em absolute} shear stress: wherever the stress vanishes, $\atau$ exhibits a corner, which manifests as a corner in the geometry. As shown in the third snapshot, this corner persists as the bodies becomes even more slender and continues to shrink. In this simulation, the body completely vanishes at a final time of $t_f = 1.79E-2$.
\todo[inline]{Is this the notation we want to use for scientific
notation? Could instead use $1.79 \times 10^{-2}$?}

To better understand the shape evolution, Fig.~\ref{shrink_intface}(a) shows several superimposed interfaces at evenly spaced times. The interfaces are color-coded by normalized time $t/t_f$. The body seems to converge to a shape that resembles an American football --- a fairly slender, for-aft symmetric shape with corners at the front and back.
Fig.~\ref{shrink_intface}(b) shows how the absolute shear stress, $\atau$, is distributed along each of these interfaces. The normalized arclength $s/L$ runs counterclockwise around the body, with $s/L = 0$ corresponding to the rear stagnation point and $s/L = 0.5$ the front stagnation point. At early times (yellow to orange), the stress is distributed non-uniformly, with highest values at the top and bottom of the body. As time proceeds, though, the stress becomes more evenly distributed along the body's surface (red). As the body nears the final stages of erosion (dark red), the stress actually becomes slightly higher near the stagnation points. A close look reveals that the stress always vanishes {\em at} the stagnation points, but in a region that becomes increasingly narrow.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.8 \textwidth]{./figs/shrink_intface.pdf}
\caption{
Shape and stress evolution: (a) Interfaces of the eroding body from Fig.~\ref{01bodseq} at evenly-spaced time intervals. Color indicates normalized time, $t/t_f$, where $t_f = 1.79E-2$ is the time at which the body completely vanishes. (b) The distribution of absolute shear stress, $\atau$, along each of these interfaces. Normalized arclength, $s/L$, runs counterclockwise from the rear stagnation point. The stress initially varies over the body's surface, but becomes more uniform over time.}
\label{shrink_intface}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-6, fixarea = 0, fixpdrop = 0
